\newpage
\subsection{Stopping time}\label{Stopping}
Let $(\Omega, \F, \F_t, \prob)$ be given, A random variable $\tau: \Omega \rightarrow [0,\infty]$ is a stopping time if 
\begin{equation*}
    \{\tau \leq t\} \in \F_t, \quad \forall t\leq T.
\end{equation*}
\textbf{Idea: At any time, we will know the event happened or not.}
\begin{thm}
Let $\F_{t+} = \bigi{\epsilon>0} \F_{t+\epsilon}$. If $\F_t = \F_{t+}$ then $\tau$  is a stopping time iff 
\begin{equation*}
    \{\tau < t\} \in \F_t, \quad \forall t\leq T.
\end{equation*}
\end{thm}
Markov/stopping time are both accepted.

\begin{rem} For function $\I{[0, \tau]}(t)$ it is both adapted and progressively measurable.
\end{rem}
\begin{example}
Brownian motion $W_t$.
\end{example}

\begin{example}
Let $X_t$ be adapted and continuous and we assume $\F_t = \F_{t+}$. Let $U$ open then $\tau = \inf \{t\geq 0; X_t \in U\}$ is a stopping time. \\
\pf Given $X_\tau \in U$, by continuity of this process,  $\exists t_n \leq t, X_{t_n} \in U$. Then \begin{equation*}
    \{\tau < t\} = \bigu{t_n \leq t} \{X_{t_n}\in U\}\in \F_t.
\end{equation*}
\qed
\end{example}

Consider theorem related to local martingale.

If $(M_t, \F_t)$ is a continuous martingale with $\sup_t \E\abs{M_t}^2 < \infty$ then the quadratic variation
\begin{equation*}
    \qvar{M}{t} = \biglim{\abs{\pi}\rightarrow 0}\bigs{k} \abs{M_{t_i} - M_{t_{i-1}}}^2
\end{equation*}
exists.
\begin{cor}
Assume $(M_t, \F_t)$ is continuous local martingale, $\tau_n \uparrow T, (M_t^{\tau_n}, \F)$ square integrable martingale. By previous theorem
\begin{equation*}
    \qvar{M^{\tau_n}}{t} \quad \text{exists}.
\end{equation*}
Now take $\tau_n \rightarrow T$ we conclude $\qvar{M}{T}$ exists
\end{cor}

\begin{example}
Let $M_t = \int_0^t X_s \diff W_s$ with condition $\int_0^T X_s^2 \diff s < \infty$ a.s. then we have
\begin{align*}
    \qvar{M}{\tau_n} &= \int_0^t X_s \I{[0,\tau_n]}(s) \diff s = \int_0^{T\land \tau_n} X_s \diff s.
 \end{align*}
 As $\tau_n \uparrow T$ we have convergence
 \begin{equation*}
     \qvar{M}{T} = \int_0^{T} X_s \diff s <\infty.
 \end{equation*}
\end{example}

\begin{thm}{(Strong Markov property)} Let $\tau$ be stopping time with $\prob(\tau < \infty) =1$ Then the new Brownian motion
\begin{equation*}
    B_t := W_{t+\tau} - W_\tau \quad t\geq 0,
\end{equation*} then, $(B_t, \setg_t)$ is a BM independent of $\F_t$\footnote{see definition on 4528 notes} with $\setg$ be defined as natural filtration.
\end{thm}
This can be used to deduce that if $(W_t, \F_t)$ be BM and $\tau$ being hitting time $\tau^a = \inf\{t\geq0; W_t = a\}$ then
\begin{equation*}
    \prob(\tau \leq t) = 2\prob (W_t \geq a),
\end{equation*} 
with density
\begin{equation*}
    f_{\tau^a} = \frac{a}{\sqrt{2\pi t^3}}\exp (-\frac{a^2}{2t}),
\end{equation*} and,
\begin{equation*}
    \E[e^{-\lambda \tau^a}] = e^{-a\sqrt{2\lambda}}, \quad \lambda > 0.
\end{equation*}

We could also study shifted Brownian motion in the sense that take $a >0, m\in \R$ and hitting time
\begin{equation*}
    \tau^a = \inf\{t\geq 0; mt + W_t \geq a\}
\end{equation*}
Then we can obtain the distribution of $\tau^a$ with its density and 
\begin{equation*}
    \prob(\tau^a < \infty) = \begin{cases}
    1 \quad &ma >0\\
    e^{2ma} \quad &ma <0
    \end{cases}
\end{equation*}
This is intuitive once you draw the picture.

\begin{thm}[Doob/ Optional Stopping Theorem]
\label{Doob} Let $(X_n, \F_n)$ be a martingale, $\tau_i, i=1,2$ be stopping times, assume that
\begin{enumerate}
    \item $\prob(\tau_1 \leq \tau_2 < \infty) = 1$,
    \item $\E|X_{\tau_i}| < \infty$,
    \item $\linf{n\rightarrow \infty} \E[|X_n|\I{\tau_i > n}] = 0, i=1,2$,
\end{enumerate}then,
\begin{equation*}
    \E(X_{\tau_2}|\F_{\tau_1}) = X_{\tau_1}.
\end{equation*}
\end{thm}
\begin{rem}
If $\tau \leq N$ a.s. (Stopping time is bounded) then optimal stopping theorem applies
\end{rem}
Example can be found at \footnote{W8 L2}.

